A Mechanised Library for Generic (Co)Programming

### 2024-02-10 paper/paper.tex
LICPICS

\documentclass{article}

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[backend=bibtex,style=alphabetic,natbib=true]{biblatex}
\addbibresource{references.bib}
\usepackage{amsmath, amssymb, amsfonts, amsthm, stmaryrd}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{mathpartir}
\usepackage{bussproofs}
\usepackage{xparse}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{lipsum}
\usepackage{xargs}
\usepackage{hyperref}
\usepackage{tikz-cd}
\usepackage{todonotes}
\usepackage{url}
\usepackage{xspace}
\usepackage{rotating}
\usepackage{quiver}
\usepackage[backend=bibtex,style=alphabetic,natbib=true]{biblatex}
\usepackage{minted}
\usepackage{newunicodechar}

\addbibresource{references.bib}
\usepackage{array}   % for \newcolumntype macro
\newcolumntype{C}{>{$}c<{$}} % math-mode version of "l" column type
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type

@@

\author{}

@@

\maketitle
\section{Introduction}
Recursive definitions cannot be proven well-defined automatically due to the
halting problem. Modern proof assistants like Coq or Agda provide a sound, but
incomplete algorithm which syntactically checks for termination or productivity.
For recursion, this is done by trying to (automatically) infer which argument in
the recursive call gets smaller with respects to the original input argument.
For productivity, the algorithm checks that the (co)recursive call appears
directly under a constructor to make sure that this function always produce at
least one element after each recursive step.

@@

Another approach to certifying termination of nonstructurally recursive
functions is the use of \emph{sized types}. Sized types were introduced in
\textcite{HughesPS96} as a way to track/verify various properties of recursive
programs, including productivity and termination. The core idea of sized types
is that types express bounds on the sizes of recursive data structures. This
approach has been used to express nonstructurally recursive algorithms in Agda:
\textcite{CopelloTB14} used sized types in a straightforward formulation of
mergesort. Such an approach has also been used in MiniAgda~\cite{abs-1202-3496}.

\printbibliography[heading=bibintoc]

\end{document}

>>>>

\documentclass[a4paper, UKenglish, cleveref, autoref, thm-restate]{lipics-v2021}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
% \usepackage[backend=bibtex,style=alphabetic,natbib=true]{biblatex}
% \usepackage[backend=bibtex,style=alphabetic,natbib=true]{biblatex}
% \addbibresource{references.bib}
\usepackage{amsmath, amssymb, amsfonts, amsthm, stmaryrd}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{mathpartir}
\usepackage{bussproofs}
\usepackage{xparse}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{lipsum}
\usepackage{xargs}
\usepackage{hyperref}
\usepackage{tikz-cd}
\usepackage{todonotes}
\usepackage{url}
\usepackage{xspace}
\usepackage{rotating}
\usepackage{quiver}
\usepackage{minted}
\usepackage{newunicodechar}

% \addbibresource{references.bib}
\usepackage{array}   % for \newcolumntype macro
\newcolumntype{C}{>{$}c<{$}} % math-mode version of "l" column type
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type

@@

\bibliographystyle{plainurl}% the mandatory bibstyle
%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

\author{Jane {Open Access}}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

\author{Joan R. Public\footnote{Optional footnote, e.g. to mark corresponding author}}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}

\authorrunning{J. Open Access and J.\,R. Public} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Jane Open Access and Joan R. Public} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
%\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}

\end{abstract}

\section{Introduction}
Recursive definitions cannot be proven well-defined automatically due to the
halting problem. Modern proof assistants like Coq or Agda provide a sound, but
incomplete algorithm which syntactically checks for termination or productivity.
For recursion, this is done by trying to (automatically) infer which argument in
the recursive call gets smaller with respects to the original input argument.
For productivity, the algorithm checks that the (co)recursive call appears
directly under a constructor to make sure that this function always produce at
least one element after each recursive step.

@@

Another approach to certifying termination of nonstructurally recursive
functions is the use of \emph{sized types}. Sized types were introduced in
\cite{HughesPS96} as a way to track/verify various properties of recursive
programs, including productivity and termination. The core idea of sized types
is that types express bounds on the sizes of recursive data structures. This
approach has been used to express nonstructurally recursive algorithms in Agda:
\cite{CopelloTB14} used sized types in a straightforward formulation of
mergesort. Such an approach has also been used in MiniAgda~\cite{abs-1202-3496}.

\bibliography{references.bib}
\end{document}
